Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-25 doc/gaia-chapter.tex
more snippets in gaia-chapter

\subsection{Order and comparison}

@@

>>>>

\subsubsection{Porting a theorem}
The \texttt{Gaia} library containsa proof that the multiplication of ordinals less than $\epsilon_0$ is associative.

\emph{From~\href{https://github.com/coq-community/gaia/blob/master/theories/ssete9.v}{gaia.ssete9.v}}

\begin{Coqsrc}
Lemma mulA: associative T1mul.
\end{Coqsrc}

This lemma was missing from \texttt{hydra-battles}. Nevertheless, we could adapt this lemma to \texttt{hydra-battles}' ordinals, by a small sequence of rewritings.

\inputsnippets{T1Bridge/multA}

The module~\href{../theories/html/gaia_hydras.T1Bridge_use.html}%
{\texttt{gaia\_hydras.T1Bridge\_use}} shows an example of
application of \texttt{multA}.

\inputsnippets{T1Bridge_use/T1BridgeUse}

\subsection{Order and comparison}
Leibniz equality and strict order on both libraries are
compatible:
\inputsnippets{T1Bridge/eqRef}

@@

\inputsnippets{T1Bridge/decideHLtRw}

Hence, both definitions of ``being in Cantor normal form'' are
compatible.

\inputsnippets{T1Bridge/nfRef}
